### 2015-07-20 src/misc/s6_thanks.tex
Updated word of thanks.

First of all, I would like to extend my thanks to \textbf{my supervisors}, Pieter and Luc, who have been of crucial importance in designing, running, and writing up the experiments in this thesis as well as to my development as a researcher in general. Thanks to \textbf{my fiancee} Daphne and \textbf{my parents}, Marja en Wim, for their unconditional support and confidence in me while I was writing this thesis. p

Second, I would like to thank \textbf{my family} Thaja, Annika, Sjors, Marcel, Senn, and Billy, Lancy, Percy, Stephanie, and Tyra, and \textbf{my friends in Boxtel \footnote{Including Lennisheuvel and Vught}} Kees, Paul, Bram, Joukje, Marieke, and Lieke.

This thesis would not have been possible without the help of 
my \textbf{collaborators} Mathieu, Paul MacNeilage, and Gerine,
the awesome people of the
\textbf{technical support group} Chi, Gerard, Mark, Norbert, Pascal, Twan, and Wilbert,
as well as the support staff
\textbf{support team} Jolanda, Maaike, Saskia, and Yvonne.
I would also like to thank the members of the 
\textbf{sensorimotor lab} Adjmal, Anouk, Antonella, Arjen, Bart, Femke, Frank, Jeroen, Joost, Julian, Jurrian, Liliana, Luc, Maaike, Mathieu, Pieter, Romy, Sara, Stan, Tineke, and Verena 
as well as our 
\textbf{trainees} Alexanra, Anna, Charlotte, Jeroen, Koen, Michael, Nynke.
Many tanks to the other people in \textbf{room B1.29}, Jurrian, Zhong Lu, and Romy, you were all great people.

During my PhD I've started to explore the world, my trips wouldn't have been as enjoyable without 
\textbf{ECVP; Alghero and Bremen} Anouk, Bronagh, Chayada, Richard, Simon-Jan, and Xuyan,
\textbf{K\"oln} Verena, Mathias, Sybrine, Marlene, and Lisa,
\textbf{Les Sybelles} Anke Marit, Lisa, Rene, Roemer, Ruud, Sasha, Sybrine, Tim, and Tjerk.
\textbf{London} Ricarda,
\textbf{Oxford} De Stagekamer; Emily, Frauke, Heleen, Katharina, Lisa, Miriam, Roemer, Susanne, and Vincent
\textbf{S\~ao Paulo} Vit\'oria and Kris,
\textbf{T\"ubbingen} Sybrine.
I would like to thank Frank and Verena in particular for the awesome trip to the \textbf{United States} that started it all.

% Johanna, Alessandra

Over the years I have participated in many sporting events and practice sessions, thanks to all those who joined me in 
\textbf{basketball} Ashley, Claudia, Flora, Jonathan, Michaelis, and Svetlana,
\textbf{climbing} Claire,
\textbf{dancing} Lies,
\textbf{running} Eelco, Corina, Stan, Sasha, Anke Marit, Tom, Jeanette, Alina, Verena Ly, Sybrine, Tim, Ruud, Rene, Tom, and Haiteng,
\textbf{squash} Gabriela,
\textbf{triathlon} Jessica and Norbert, 
\textbf{volleyball} Arjen, Christian, Egbert, Florian, Loes, Maaike, Mark, Marlene, Marvin, Pascal de W., Pascal B., Kors, Roemer, Ruud, Sanne, Sara, Sarah, Sasha, Sebo, and Sybrine, 
and 
\textbf{walking} Anke-Marit, Alina, Erik, Johanna, Sebastiaan, Laurence, Mirjam, Desiree, and Bart.

Finally, I would like to thank everyone who did not fit in any of the above categories.

>>>>

Many people have contributed to my social and professional development over the course of my PhD. I would therefore like to extend my thanks to my friends, colleagues, and family for a wonderful six years.

\textbf{Pieter}, you are an amazing researcher and I'm proud to have been your student. I admire your sense of pragmatism and focus. And, I must admit that, even though our (sometimes heated) discussions, you have greatly influenced my writing style for the better. \textbf{Luc}, you greatly helped me iron out the detail in my experimental procedures, and provided crucial feedback when I was stuck analyzing our data. After receiving yet another batch of comments on one of my manuscripts, you were always there to provide support and to help me formulate a proper response. Many thanks to both of you!

In addition to \textbf{Pieter} and \textbf{Luc}, our collaborators \textbf{Mathieu}, \textbf{Maaike}, \textbf{Jan}, and \textbf{Paul} as well as the \textbf{technical support group} have played a crucial role in designing, setting up, running, and writing the experiments in this thesis. Thanks!

As with everything in life, writing this thesis was not always easy. Thanks to \textbf{Daphne} and my parents, \textbf{Marja and Wim}, for their unconditional support and confidence in me while I was writing this thesis.
